|

### 2019-10-06 manuscript/manuscript.Rmd
wrap up interp section

We motivate our discussion by considering several aspects of interpretability. For the time being, one can take any of the definitions cited above. As we proceed through the points below, we aim to arrive at a more scoped and relevant definition of what it means to attain interpretability in a pricing model. (TODO: add a sentence mapping out what we'll talk about in this section)

@@

An occasional misconception is that we have no visibility into how some ML models *compute* predictions, which render them uninterpretable. Outside of proprietary algorithms, all common ML models, including neural networks, gradient boosted trees, and random forests, are well studied and have large bodies of literature documenting their inner workings. As an example, a fitted neural network model on tabular data is simply a composition of linear transformations followed with nonlinear activation functions. As in Equation \ref{eq:badglm}, one can write down the mathematical equation for calculating the prediction given some inputs, but it may be difficult for a human to reason about it. This is a somewhat philosophical point, as we show later in the paper that we can still provide explanations of completely "black box" models, but is important to note given that pricing models undergo regulatory scrutiny.

## Explanations are Social

Proposed by @hiltonConversationalProcesses1990 and interpreted by @millerExplanationArtificial2017 in the context of ML, model explanations are conversations or social interactions. One consequence of this identification is that explanations need to be *relevant* to the *audience*. In developing, filing, and operationalizing a pricing model, one needs to accommodate a variety of stakeholders, each of whom has a different set of questions, assumptions, and technical capacity. First, there are internal stakeholders at the company, which includes management and underwriters. While some of the individuals in this audience may be technical, they are likely less familiar with predictive modeling techniques than the actuaries and data scientists who build the models. (TODO: what's a representative question here?) Next, we have the regulators, who may have limited resources to review the models, and will focus on a specific list of questions.

>>>>

We motivate our discussion by considering several aspects of interpretability. As we proceed through the points below, we aim to arrive at a more scoped and relevant definition of what it means to attain interpretability in a pricing model. We first clarify a couple concepts regarding interpretable *classes* of models and and the computational transparency of ML models. We then emphasize findings on the social aspects of ML explanations most relevant to our use case. With the provided background, we discuss a potential framework for implementing ML interpretability in practice.

@@

Another occasional misconception is that we have no visibility into how some ML models *compute* predictions, which render them uninterpretable. Outside of proprietary algorithms, all common ML models, including neural networks, gradient boosted trees, and random forests, are well studied and have large bodies of literature documenting their inner workings. As an example, a fitted neural network model on tabular data is simply a composition of linear transformations followed with nonlinear activation functions. As in Equation \ref{eq:badglm}, one can write down the mathematical equation for calculating the prediction given some inputs, but it may be difficult for a human to reason about it. We show later that we can still provide explanations of completely "black box" models, but is important to note that ML model predictions are still governed by mathematical rules, given that pricing models undergo regulatory scrutiny.

## Explanations are Contextual

Proposed by @hiltonConversationalProcesses1990 and interpreted by @millerExplanationArtificial2017 in the context of ML, model explanations are conversations or social interactions. One consequence of this identification is that explanations need to be *relevant* to the *audience*. In developing, filing, and operationalizing a pricing model, one needs to accommodate a variety of stakeholders, each of whom has a different set of questions, assumptions, and technical capacity. First, there are internal stakeholders at the company, which includes management and underwriters. While some of the individuals in this audience may be technical, they are likely less familiar with predictive modeling techniques than the actuaries and data scientists who build the models. Next, we have the regulators, who may have limited resources to review the models, and will focus on a specific list of questions. Finally, we have the public, who has an interest (perhaps more so than the other parties) because their lives are directly affected by the premiums charged.

It is interesting to note that, the modelers, who are most familiar with the models, tend to be same people designing and communicating the explanations. This poses a challenge that @millerExplainableAI2017 calls "inmates running the asylum", where the modelers design explanations for *themselves* rather than the intended audience.

Another point outlined in Miller's survey [@millerExplanationArtificial2017] is that explanations are *contrastive*. In other words, people are often interested in not why something happened, but rather why it happened instead of something else. For example, policyholders might not care exactly how their auto premiums are computed, but would like to know why they are being charged more than their coworkers who drive similar vehicles. As an extension, policyholders may want to know what they can change in order to obtain lower premiums.

## Asking and Answering the Right Questions

With the above considerations in mind, we propose a potential framework for interpreting ML models for insurance pricing. The actuarial profession, in collaboration with regulators, define a set of questions to be answered by explanations accompanying ML models, along with acceptance criteria and examples of successful explanations. In other words, interpretability for our purposes is defined as the ability of a model's explanations to answer the posed questions.

These questions should relate to existing guidelines, such as those described in @naic_white_paper and outlined in Section \ref{need}, standards of practice, and regulation, and in fact should not be specific only to ML models. By standardizing on a set of questions, we reduce the burden of both companies and regulators; this is especially important for the latter, who are already resource constrained facing increasing variety of models being filed. This format should also be familiar to actuaries who are accustomed to adhering to specific guidelines in, for example, ASOPs. Like the ASOPs, We envision that these questions and guidelines will be continually updated to reflect feedback obtained and advances in research.

While the realization of a set of such guidelines is an ambitious undertaking beyond the scope of this paper, we present in the next section a sample set of questions and techniques one can leverage to answer them. The goal of these case studies is twofold: to more concretely illustruate the proposed framework, and to expose the actuarial audience to modern ML interpretation techniques.
